---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

#Description#

Plot single and multi-facet quality control charts within the ggplot framework using stat_QC and stat_mR. Calculate quality control limits using QC_Lines.

Methods supported:

  * **Individuals Charts** : mR, XmR
  * **Attribute Charts ** : c, np, p, u
  * **Studentized Charts**: xBar.rBar, xBar.rMedian, xBar.sBar, xMedian.rBar, xMedian.rMedian
  * **Dispersion Charts**: rBar, rMedian, sBar


#Example#

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r}
library(ggplot2)
library(ggQC)


set.seed(5555)
Golden_Egg_df <- data.frame(month=1:12,
                 egg_diameter = rnorm(n = 12, mean = 1.5, sd = 0.2)
                 )

XmR_Plot <- ggplot(Golden_Egg_df, aes(x = month, y = egg_diameter)) +
               geom_point() + geom_line() + 
               stat_QC(method = "XmR")

XmR_Plot
```

#Installation#

  * cran: install.package("ggQC")
  * github: devtools::install_github("kenithgrey/ggQC")

#Overview#

 * QC_Lines() : Output quality control chart data in table format
 * stat_QC()  : ggplot stat to generate control charts supported methods
 * stat_mR(): ggplot stat to generate mR chart.
 * stat_QC_labels(): ggplot stat to write text labels on control chart center line and limits. 
 * 30 plus functions to calculate specific control chart constants. (recommend using QC_Lines()) 
