---
title: "ggQC::stat_QC()"
author: "Kenith Grey"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ggQC::stat_QC()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

***
#Description#

Produce QC charts with ggplot framework. Support for faceting and layering of multiple QC chart lines on a single plot. Charts supported (see method argument for call):

  * Individuals Charts: mR, XmR,

  * Attribute Charts: c, np, p, u,

  * Studentized Charts: xBar.rBar, xBar.rMedian, xBar.sBar, xMedian.rBar, xMedian.rMedian,

  * Dispersion Charts: rBar, rMedian, sBar.

To label chart lines see stat_QC_labels

#Usage#

    stat_QC(mapping = NULL, data = NULL, geom = "hline",
            position = "identity", na.rm = FALSE, show.legend = NA,
            inherit.aes = TRUE, n = NULL, method = "xBar.rBar",
            color.qc_limits = "red", color.qc_center = "green", ...)

#ggplot Standard Arguments#

**mapping**: Set of aesthetic mappings created by aes or aes_. If specified and inherit.aes = TRUE (the default), it is combined with the default mapping at the top level of the plot. You must supply mapping if there is no plot mapping.

**data**: The data to be displayed in this layer. There are three options:
If NULL, the default, the data is inherited from the plot data as specified in the call to ggplot.

A data.frame, or other object, will override the plot data. All objects will be fortified to produce a data frame. See fortify for which variables will be created.
A function will be called with a single argument, the plot data. The return value must be a data.frame., and will be used as the layer data.

**geom**: The geometric object to use display the data

**position**: Position adjustment, either as a string, or the result of a call to a position adjustment function.

**na.rm**:	a logical value indicating whether NA values should be stripped before the computation proceeds.

**show.legend**:	logical. Should this layer be included in the legends? NA, the default, includes if any aesthetics are mapped. FALSE never includes, and TRUE always includes.

**inherit.aes**: If FALSE, overrides the default aesthetics, rather than combining with them. This is most useful for helper functions that define both data and aesthetics and shouldn't inherit behaviour from the default plot specification, e.g. borders.

#Specialized Arguments#
**n**: number, for

  * Studentized Charts, used for custom or hypothetical subgroup size.
  * np Charts, used to specify a fixed area of opportunity.

**method** : string, calling the following methods:

  * **Individuals Charts**: mR, XmR,
  * **Attribute Charts**: c, np, p, u,
  * **Studentized Charts**: xBar.rBar, xBar.rMedian, xBar.sBar, xMedian.rBar, xMedian.rMedian
  * **Dispersion Charts**: rBar, rMedian, sBar.

**color.qc_limits**	: color, used to colorize the plot's upper and lower mR control limits.

**color.qc_center**	: color, used to colorize the plot's center line.

**...**: other arguments passed on to layer. These are often aesthetics, used to set an aesthetic to a fixed value, like color = "red" or size = 3. They may also be parameters to the paired geom/stat.

***

#Examples#
```{r, include=FALSE}
require(ggplot2)
require(ggQC)
```

```{r Setup Data}
# Setup Data --------------------------------------------------------------
set.seed(5555)
Process1 <- data.frame(processID = as.factor(rep(1,100)),
                       metric_value = rnorm(100,0,1),
                       subgroup_sample=rep(1:20, each=5),
                       Process_run_id = 1:100)
set.seed(5555)
Process2 <- data.frame(processID = as.factor(rep(2,100)),
                       metric_value = rnorm(100,5, 1),
                       subgroup_sample=rep(1:10, each=10),
                       Process_run_id = 101:200)
Both_Processes <- rbind(Process1, Process2)
```

###Basic XmR Chart###
```{r Basic XmR, fig.width=7}
XmR <- ggplot(Process1, aes(x=Process_run_id, y = metric_value)) +
       geom_point() + geom_line() + 
       stat_QC(method="XmR") 
XmR
XmR

```

###Basic XmR Chart - Adding Labels###
```{r Basic XmR add Labels, fig.width=7}
XmR + stat_QC_labels(method="XmR")
```

###Basic XmR Chart - Change Digits###
```{r Basic XmR add Labels Digits, fig.width=7}
XmR + stat_QC_labels(method="XmR", digits = 3)
```


